Fluent statistical computing interfaces for biological data analysis

### 2020-07-16 Rmd/01-intro.Rmd
update text

This thesis focuses on core aspects of EDA as part of a biological data
science workflow: wrangling, integration and visualisation, with a focus 
on applications to genomics and transcriptomics. To begin we discuss wrangling
biological data using a coherent representation and programming interface; 
section \@ref(sec:tidygranges)
introduces a grammar-based framework for transforming genomics data that is 
described in chapter \@ref(ch:plyranges). We then look at integrating data and 
model outputs over genomic regions to gain biological insight; \@ref(sec:intron) 
introduces a framework for incorporating genomic regions over multiple assays, 
described in chapter \@ref(ch:fluentGenomics), while \@ref(sec:coverage)
discusses finding 'interesting' genomic regions via multiple summaries of a 
single assay, described in \@ref(ch:intron). Next, we consider the challenges in 
visualising  high dimensional data; section \@ref(sec:va) introduces an 
interactive visualisation approach for understanding non-linear dimension 
reduction  techniques described in chapter \@ref(ch:tsne). Lastly, in chapter 
\@ref(ch:conclusion) I describe the outputs of my thesis and plans for future 
developments.

>>>>

This thesis focuses on core aspects of EDA as part of a biological data
science workflow: wrangling, integration and visualisation, with a focus 
on applications to genomics and transcriptomics. To begin we discuss wrangling
biological data using a coherent representation and programming interface; 
section \@ref(sec:tidygranges)
introduces a grammar-based framework for transforming genomics data that is 
described in chapter \@ref(ch:plyranges). We then look at integrating data and 
model outputs over genomic regions to gain biological insight; 
\@ref(sec:integrate) introduces a framework for incorporating genomic regions 
over multiple assays, described in chapter \@ref(ch:fluentGenomics), while 
\@ref(sec:coverage) discusses finding 'interesting' genomic regions via 
multiple summaries of a single assay, described in \@ref(ch:intron). Next, we 
consider the challenges in  visualising  high dimensional data; section 
\@ref(sec:va) introduces an  interactive visualisation approach for 
understanding non-linear dimension reduction  techniques described in chapter 
\@ref(ch:tsne). Lastly, in chapter \@ref(ch:conclusion) I describe the outputs 
of my thesis and plans for future developments.

### 2020-07-16 Rmd/03-fluentGenomics.Rmd
update toc; rebuild
update text

```{r fluentGenomics-init, echo = FALSE, cache = FALSE, include = FALSE}
knitr::read_chunk(here::here("scripts", "fluentGenomics.R"))
```

@@

## Acknowledgements

>>>>

```{r fluentGenomics-init, echo = FALSE, cache = FALSE, include = FALSE}
knitr::opts_chunk$set(cache = TRUE)
knitr::read_chunk(here::here("scripts", "fluentGenomics.R"))
```

@@

## Acknowledgements {-}
